SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-09-08 scipy-1.0/paper.tex
Cite astropy in broader community section draft.

>>>>

The scientific Python ecosystem includes many examples
of domain-specific software libraries building on top
of SciPy features, and then returning to the base SciPy library
to suggest and even implement improvements to enable
more effective science applications. For example, there
are common contributors to the SciPy and astropy core
libraries\cite{astropy-2018}, and what works well for 
one of the code bases, infrastructures, or communities 
is often transferred in some form to the other.
